---
title: "Simulation Report"
subtitle: "NetSimR Claims & Reinsurance Simulator"
date: "Generated `r format(Sys.time(), '%d %B %Y, %H:%M')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
    toc_depth: 2
    theme:
      version: 5
      preset: "bootstrap"
      primary: "#2563eb"
      base_font: "system-ui, -apple-system, Segoe UI, Roboto, Helvetica Neue, Arial, sans-serif"
      heading_font: "system-ui, -apple-system, Segoe UI, Roboto, Helvetica Neue, Arial, sans-serif"
params:
  numOfSimulations: NULL
  freq_params: NULL
  sev_params: NULL
  seedSetBinary: NULL
  seedValue: NULL
  freqDistr: NULL
  sevDistr: NULL
  paretoSlice: NULL
  pareto_slice_times: NULL
  slice_pareto_alphas: NULL
  slice_pareto_x_ms: NULL
  sevCapBinary: NULL
  sev_cap_amount: NULL
  reinsuranceStructureEEL: NULL
  reinsurance_structure_eel_dedctible_amount: NULL
  reinsurance_structure_eel_limit_amount: NULL
  reinsuranceStructureAL: NULL
  reinsurance_structure_al_dedctible_amount: NULL
  reinsurance_structure_al_limit_amount: NULL
  multiprocessing: NULL
  reinsuranceStructureLimitedReinstatements: NULL
  reinsuranceStructureReinstatementLimit: NULL
  total_claims_data: NULL
  freq_distr_label: NULL
  sev_distr_label: NULL
  freq_param_labels: NULL
  sev_param_labels: NULL
---

```{css, echo = FALSE}
:root {
  --r-navy: #0b1f3d;
  --r-blue: #2563eb;
  --r-blue-soft: #eff6ff;
  --r-red: #dc2626;
  --r-border: #e2e8f0;
  --r-muted: #64748b;
  --r-text: #0f172a;
  --r-label: #334155;
  --r-shadow: 0 1px 2px rgba(15, 23, 42, 0.04), 0 6px 18px rgba(15, 23, 42, 0.05);
}

body {
  font-family: "Inter", "Segoe UI", system-ui, -apple-system, Roboto, "Helvetica Neue", Arial, sans-serif;
  color: var(--r-text);
  background: #f1f5f9;
  font-size: 15px;
  line-height: 1.55;
}

.main-container {
  max-width: 1180px;
}

/* ---------- Header banner ---------- */
#header {
  display: flex;
  flex-direction: column;
  background:
    radial-gradient(circle at 88% 15%, rgba(96, 165, 250, 0.35), transparent 45%),
    linear-gradient(135deg, #0b1f3d 0%, #13315c 60%, #1d4ed8 140%);
  color: #ffffff;
  border-radius: 18px;
  padding: 28px 32px;
  margin: 24px 0 8px 0;
  box-shadow: var(--r-shadow);
}

#header h1.title {
  color: #ffffff;
  font-weight: 800;
  font-size: 2.1rem;
  letter-spacing: -0.02em;
  margin: 0;
}

#header .subtitle {
  order: -1;
  color: #93c5fd;
  font-size: 0.78rem;
  font-weight: 800;
  text-transform: uppercase;
  letter-spacing: 0.1em;
  margin: 0 0 8px 0;
}

#header .date {
  color: rgba(255, 255, 255, 0.75);
  font-size: 0.92rem;
  font-weight: 500;
  margin: 8px 0 0 0;
}

/* ---------- Headings ---------- */
h2 {
  font-weight: 800;
  font-size: 1.35rem;
  letter-spacing: -0.01em;
  margin: 36px 0 14px 0;
  padding-bottom: 8px;
  border-bottom: 1px solid var(--r-border);
}

h3 {
  font-size: 1rem;
  font-weight: 700;
  color: var(--r-label);
  margin: 0 0 10px 0;
}

.section-intro {
  color: var(--r-muted);
  margin: -4px 0 14px 0;
}

/* ---------- Headline figures ---------- */
.kpi-grid {
  display: grid;
  grid-template-columns: repeat(3, minmax(0, 1fr));
  gap: 12px;
}

@media (max-width: 767px) {
  .kpi-grid { grid-template-columns: repeat(2, minmax(0, 1fr)); }
}

@media (max-width: 420px) {
  .kpi-grid { grid-template-columns: 1fr; }
}

.kpi {
  background: #ffffff;
  border: 1px solid var(--r-border);
  border-top: 3px solid var(--r-blue);
  border-radius: 14px;
  padding: 14px 16px;
  box-shadow: var(--r-shadow);
}

.kpi.kpi-tail {
  border-top-color: var(--r-red);
}

.kpi-label {
  font-size: 0.72rem;
  font-weight: 800;
  letter-spacing: 0.07em;
  text-transform: uppercase;
  color: var(--r-muted);
}

.kpi-value {
  font-size: 1.4rem;
  font-weight: 800;
  margin-top: 4px;
  font-variant-numeric: tabular-nums;
  white-space: nowrap;
  overflow: hidden;
  text-overflow: ellipsis;
}

.kpi-note {
  font-size: 0.8rem;
  color: var(--r-muted);
  margin-top: 2px;
}

/* ---------- Settings ---------- */
.settings-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(260px, 1fr));
  gap: 12px;
}

.setting-card {
  background: #ffffff;
  border: 1px solid var(--r-border);
  border-radius: 14px;
  padding: 14px 16px;
  box-shadow: var(--r-shadow);
}

.setting-title {
  display: flex;
  align-items: center;
  gap: 8px;
  font-weight: 800;
  margin-bottom: 10px;
}

.setting-title::before {
  content: "";
  width: 8px;
  height: 8px;
  border-radius: 50%;
  background: var(--r-blue);
}

.setting-card dl {
  display: grid;
  grid-template-columns: auto 1fr;
  gap: 6px 14px;
  margin: 0;
}

.setting-card dt {
  font-weight: 600;
  font-size: 0.88rem;
  color: var(--r-muted);
}

.setting-card dd {
  margin: 0;
  text-align: right;
  font-weight: 600;
  font-variant-numeric: tabular-nums;
}

.setting-card .setting-off {
  color: var(--r-muted);
  font-weight: 500;
}

/* ---------- Tables ---------- */
.two-col {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(320px, 1fr));
  gap: 16px;
  align-items: start;
}

.table-card {
  background: #ffffff;
  border: 1px solid var(--r-border);
  border-radius: 14px;
  padding: 14px 16px 6px 16px;
  box-shadow: var(--r-shadow);
  overflow-x: auto;
}

.report-table {
  width: 100%;
  margin: 0 0 8px 0;
  font-variant-numeric: tabular-nums;
}

.report-table thead th {
  font-size: 0.72rem;
  font-weight: 800;
  text-transform: uppercase;
  letter-spacing: 0.06em;
  color: var(--r-muted);
  border-bottom: 1px solid var(--r-border) !important;
  background: transparent;
}

.report-table td {
  border-top: 1px solid #f1f5f9;
  padding-top: 7px;
  padding-bottom: 7px;
}

.report-table tbody tr:hover td {
  background: #f8fafc;
}

/* ---------- Charts ---------- */
.chart-card {
  background: #ffffff;
  border: 1px solid var(--r-border);
  border-radius: 14px;
  padding: 16px 18px 10px 18px;
  margin-bottom: 16px;
  box-shadow: var(--r-shadow);
}

.chart-card p {
  margin: 0;
}

.chart-card img {
  max-width: 100%;
  height: auto;
}

.chart-note {
  color: var(--r-muted);
  font-size: 0.85rem;
  margin: 0 0 8px 0;
}

/* ---------- Notes and footer ---------- */
.callout {
  background: var(--r-blue-soft);
  border: 1px solid #bfdbfe;
  border-left: 4px solid var(--r-blue);
  border-radius: 12px;
  padding: 14px 18px;
}

.callout ul {
  margin: 0;
  padding-left: 1.1rem;
}

.callout li + li {
  margin-top: 4px;
}

.report-footer {
  color: var(--r-muted);
  font-size: 0.85rem;
  text-align: center;
  margin: 32px 0 24px 0;
}

/* ---------- Table of contents ---------- */
.tocify {
  border: 1px solid var(--r-border);
  border-radius: 14px;
  background: #ffffff;
  box-shadow: var(--r-shadow);
  margin-top: 24px;
}

.tocify .list-group-item {
  border: 0;
  font-size: 0.9rem;
}

.tocify .list-group-item.active {
  background: var(--r-blue);
  border-radius: 8px;
}

@media print {
  #TOC, .tocify { display: none; }
  body { background: #ffffff; }
  .kpi, .setting-card, .table-card, .chart-card { box-shadow: none; break-inside: avoid; }
  #header { -webkit-print-color-adjust: exact; print-color-adjust: exact; }
}
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE,
  fig.width = 9, fig.height = 4.2, fig.retina = 2, dpi = 96
)

div <- htmltools::div
tags <- htmltools::tags

claims <- as.numeric(params$total_claims_data)

# ---------- formatting helpers ----------
is_blank <- function(x) is.null(x) || length(x) == 0 || all(is.na(x))
fmt_num <- function(x, digits = 2) {
  if (is_blank(x)) return("—")
  formatC(as.numeric(x), format = "f", digits = digits, big.mark = ",")
}
fmt_int <- function(x) if (is_blank(x)) "—" else formatC(round(as.numeric(x)), format = "d", big.mark = ",")
fmt_pct <- function(x, digits = 1) paste0(formatC(100 * x, format = "f", digits = digits), "%")
# headline amounts use one decimal style for the whole report, set by the scale of the results
amount_digits <- if (isTRUE(max(abs(as.numeric(params$total_claims_data)), na.rm = TRUE) >= 1000)) 0 else 2
fmt_amount <- function(x) {
  if (is_blank(x)) return("—")
  fmt_num(x, amount_digits)
}
fmt_return_period <- function(p) paste("1 in", formatC(round(1 / (1 - p)), format = "d", big.mark = ","))
label_or_id <- function(label, id) {
  if (!is_blank(label)) return(label)
  if (!is_blank(id)) return(gsub("_", " ", id))
  "—"
}
param_text <- function(values, labels) {
  values <- unlist(values)
  if (is_blank(values)) return("—")
  shown <- fmt_num(values, 4)
  shown <- sub("\\.?0+$", "", shown)
  if (!is_blank(labels) && length(labels) == length(values)) {
    # non-breaking spaces keep each "name = value" pair on one line
    nbsp <- intToUtf8(160)
    paste(paste(labels, shown, sep = paste0(nbsp, "=", nbsp)), collapse = ", ")
  } else {
    paste(shown, collapse = ", ")
  }
}

# ---------- statistics ----------
quantile_of <- function(p) unname(stats::quantile(claims, p, na.rm = TRUE))
# TVaR as the average of the worst (1 - p) share of simulations; unlike averaging
# everything at or above VaR, this stays correct when many totals tie (e.g. at zero)
claims_desc <- sort(claims[!is.na(claims)], decreasing = TRUE)
tvar_of <- function(p) mean(claims_desc[seq_len(max(1, ceiling(length(claims_desc) * (1 - p))))])
claims_mean <- mean(claims, na.rm = TRUE)
claims_sd <- stats::sd(claims, na.rm = TRUE)
var995 <- quantile_of(0.995)
tvar995 <- tvar_of(0.995)

# ---------- chart helpers ----------
col_blue <- "#3b82f6"
col_blue_dark <- "#1d4ed8"
col_navy <- "#0f172a"
col_red <- "#dc2626"
col_grid <- "#e2e8f0"
col_muted <- "#64748b"

chart_par <- function(mar = c(4.2, 5.6, 1, 1)) {
  graphics::par(mar = mar, mgp = c(3.4, 0.7, 0), las = 1, col.axis = col_muted,
                col.lab = "#334155", fg = col_muted, cex.axis = 0.85, cex.lab = 0.95)
}
axis_labels <- function(at) {
  if (max(abs(at), na.rm = TRUE) >= 100) formatC(at, format = "f", digits = 0, big.mark = ",") else format(at)
}
x_axis <- function(at) graphics::axis(1, at = at, labels = axis_labels(at), col = col_grid, col.ticks = col_grid)

# layers that are rarely hit produce many zero totals; a single bar at zero would flatten
# the histogram and box plot, so those charts show the non-zero totals and state the zero share
zero_share <- mean(claims == 0, na.rm = TRUE)
drop_zeros <- isTRUE(zero_share >= 0.2) && any(claims > 0, na.rm = TRUE)
plot_claims <- if (drop_zeros) claims[!is.na(claims) & claims > 0] else claims[!is.na(claims)]
zero_note <- if (drop_zeros) {
  paste0(" ", fmt_pct(zero_share), " of simulations had zero total claims and are left out of this chart.")
} else {
  ""
}
```

## Key results

<p class="section-intro">Total claims per simulated period, after the tail adjustments and reinsurance structures below.</p>

```{r kpis}
tile <- function(label, value, note = NULL, class = "kpi") {
  div(class = class,
      div(class = "kpi-label", label),
      div(class = "kpi-value", value),
      if (!is.null(note)) div(class = "kpi-note", note))
}

div(
  class = "kpi-grid",
  tile("Mean", fmt_amount(claims_mean), paste(fmt_int(length(claims)), "simulations")),
  tile("Median", fmt_amount(quantile_of(0.5))),
  tile("Standard deviation", fmt_amount(claims_sd),
       if (isTRUE(claims_mean != 0)) paste("CV", fmt_num(claims_sd / claims_mean))),
  tile("VaR 99.5%", fmt_amount(var995), fmt_return_period(0.995), class = "kpi kpi-tail"),
  tile("TVaR 99.5%", fmt_amount(tvar995), "Average beyond VaR 99.5%", class = "kpi kpi-tail"),
  tile("Maximum", fmt_amount(max(claims, na.rm = TRUE)), "Largest simulated total")
)
```

## Model settings

```{r settings}
setting_card <- function(title, rows) {
  rows <- rows[!vapply(rows, is.null, logical(1))]
  div(
    class = "setting-card",
    div(class = "setting-title", title),
    tags$dl(lapply(names(rows), function(key) {
      htmltools::tagList(tags$dt(key), tags$dd(rows[[key]]))
    }))
  )
}
off <- function(text = "Not applied") tags$span(class = "setting-off", text)

has_deductible <- function(structure) isTRUE(structure %in% c("Unlimited Layer", "Limited Layer", "Exclude Layer"))
has_limit <- function(structure) isTRUE(structure %in% c("Limited Layer", "Exclude Layer"))

eel <- params$reinsuranceStructureEEL
al <- params$reinsuranceStructureAL
slice_count <- if (isTRUE(params$paretoSlice)) as.integer(params$pareto_slice_times) else 0L
slice_rows <- if (slice_count > 0) {
  alphas <- unlist(params$slice_pareto_alphas)
  x_ms <- unlist(params$slice_pareto_x_ms)
  stats::setNames(
    lapply(seq_len(slice_count), function(j) {
      paste0("α ", fmt_num(alphas[j], 2), " from ", fmt_num(x_ms[j], if (abs(x_ms[j]) >= 1000) 0 else 2))
    }),
    paste("Pareto slice", seq_len(slice_count))
  )
} else {
  list("Pareto slices" = off())
}

div(
  class = "settings-grid",
  setting_card("Simulation", list(
    "Simulations" = fmt_int(params$numOfSimulations),
    "Seed" = if (isTRUE(params$seedSetBinary)) paste("Fixed at", params$seedValue) else off("Random"),
    "Processing" = if (isTRUE(params$multiprocessing)) "Parallel" else "Single process"
  )),
  setting_card("Frequency", list(
    "Distribution" = label_or_id(params$freq_distr_label, params$freqDistr),
    "Parameters" = param_text(params$freq_params, params$freq_param_labels)
  )),
  setting_card("Severity", list(
    "Distribution" = label_or_id(params$sev_distr_label, params$sevDistr),
    "Parameters" = param_text(params$sev_params, params$sev_param_labels)
  )),
  setting_card("Tail adjustments", c(
    slice_rows,
    list("Severity cap" = if (isTRUE(params$sevCapBinary)) fmt_amount(params$sev_cap_amount) else off())
  )),
  setting_card("Each & every loss (EEL)", list(
    "Structure" = if (is_blank(eel) || eel == "No Reinsurance Structure") off("None") else eel,
    "Deductible" = if (has_deductible(eel)) fmt_amount(params$reinsurance_structure_eel_dedctible_amount),
    "Limit" = if (has_limit(eel)) fmt_amount(params$reinsurance_structure_eel_limit_amount),
    "Reinstatements" = if (isTRUE(eel == "Limited Layer")) {
      if (isTRUE(params$reinsuranceStructureLimitedReinstatements)) {
        paste("Up to", fmt_int(params$reinsuranceStructureReinstatementLimit))
      } else {
        off("Unlimited")
      }
    }
  )),
  setting_card("Aggregate layer (AL)", list(
    "Structure" = if (is_blank(al) || al == "No Reinsurance Structure") off("None") else al,
    "Deductible" = if (has_deductible(al)) fmt_amount(params$reinsurance_structure_al_dedctible_amount),
    "Limit" = if (has_limit(al)) fmt_amount(params$reinsurance_structure_al_limit_amount)
  ))
)
```

## Statistics and tail risk

```{r stats-tables}
summary_stats <- data.frame(
  Metric = c("Simulations", "Mean", "Median", "Standard deviation", "Coefficient of variation", "Minimum", "Maximum"),
  Value = c(
    fmt_int(length(claims)),
    fmt_num(claims_mean),
    fmt_num(quantile_of(0.5)),
    fmt_num(claims_sd),
    if (isTRUE(claims_mean != 0)) fmt_num(claims_sd / claims_mean, 3) else "—",
    fmt_num(min(claims, na.rm = TRUE)),
    fmt_num(max(claims, na.rm = TRUE))
  )
)

probs <- c(0.5, 0.75, 0.9, 0.95, 0.975, 0.99, 0.995)
tail_table <- data.frame(
  Percentile = fmt_pct(probs),
  `Return period` = vapply(probs, fmt_return_period, character(1)),
  VaR = vapply(probs, function(p) fmt_num(quantile_of(p)), character(1)),
  TVaR = vapply(probs, function(p) fmt_num(tvar_of(p)), character(1)),
  check.names = FALSE
)

as_table <- function(df, align) {
  htmltools::HTML(as.character(knitr::kable(
    df, format = "html", align = align, escape = TRUE,
    table.attr = 'class="table table-sm report-table"'
  )))
}

div(
  class = "two-col",
  div(class = "table-card", tags$h3("Summary statistics"), as_table(summary_stats, c("l", "r"))),
  div(class = "table-card", tags$h3("Percentiles, VaR and TVaR"), as_table(tail_table, c("l", "l", "r", "r")))
)
```

## Charts

::: {.chart-card}
### Distribution of total claims
<p class="chart-note">Dashed lines mark the mean and the 99.5% VaR of all simulations.`r zero_note`</p>

```{r hist-plot}
chart_par()
h <- graphics::hist(plot_claims, breaks = 80, plot = FALSE)
y_top <- max(h$counts) * 1.1
plot(h, col = NA, border = NA, main = "", xlab = "Total claims", ylab = "Simulations",
     axes = FALSE, ylim = c(0, y_top))
y_at <- pretty(c(0, y_top))
graphics::abline(h = y_at, col = col_grid, lwd = 0.8)
plot(h, col = col_blue, border = "white", add = TRUE)
x_axis(pretty(h$breaks))
graphics::axis(2, at = y_at, labels = formatC(y_at, format = "d", big.mark = ","), lwd = 0)
graphics::abline(v = claims_mean, col = col_navy, lty = 2, lwd = 1.8)
graphics::abline(v = var995, col = col_red, lty = 2, lwd = 1.8)
graphics::legend("topright", bty = "n", cex = 0.85, text.col = "#334155", lty = 2, lwd = 1.8,
                 col = c(col_navy, col_red),
                 legend = c(paste("Mean", fmt_amount(claims_mean)), paste("VaR 99.5%", fmt_amount(var995))))
```
:::

::: {.chart-card}
### Spread and outliers
<p class="chart-note">The box covers the middle 50% of simulations; dots are outliers.`r zero_note`</p>

```{r boxplot-plot, fig.height = 2.3}
chart_par(mar = c(4.2, 1.5, 0.6, 1))
graphics::boxplot(plot_claims, horizontal = TRUE, axes = FALSE, frame.plot = FALSE,
                  col = "#dbeafe", border = col_blue_dark, medcol = col_navy, medlwd = 2.4,
                  whisklty = 1, staplelwd = 1.2, outpch = 16, outcex = 0.35,
                  outcol = grDevices::adjustcolor(col_blue_dark, alpha.f = 0.25),
                  xlab = "Total claims")
x_axis(pretty(range(plot_claims)))
```
:::

::: {.chart-card}
### Cumulative distribution
<p class="chart-note">Share of simulations with total claims at or below each amount.</p>

```{r ecdf-plot}
chart_par()
cdf_probs <- seq(0, 1, length.out = 1001)
cdf_x <- stats::quantile(claims, cdf_probs, na.rm = TRUE, names = FALSE)
plot(cdf_x, cdf_probs, type = "n", axes = FALSE, main = "",
     xlab = "Total claims", ylab = "Cumulative probability", ylim = c(0, 1))
graphics::abline(h = seq(0, 1, 0.25), col = col_grid, lwd = 0.8)
graphics::abline(v = var995, col = col_red, lty = 2, lwd = 1.5)
graphics::lines(cdf_x, cdf_probs, type = "s", col = col_blue, lwd = 2.4)
x_axis(pretty(range(cdf_x)))
graphics::axis(2, at = seq(0, 1, 0.25), labels = paste0(seq(0, 100, 25), "%"), lwd = 0)
```
:::

## How to read this report

::: {.callout}
- A large gap between the median and the tail percentiles points to a heavy-tailed outcome.
- VaR is the loss exceeded only with the stated probability. TVaR is the average loss in those worst cases, so it is always at least as large as VaR.
- The return period shows the same probability as a frequency: 99.5% corresponds to a 1 in 200 year event.
- Figures reflect total claims after any tail adjustments and reinsurance structures listed under Model settings.
:::

<div class="report-footer">
Generated with NetSimR`r tryCatch(paste0(" ", utils::packageVersion("NetSimR")), error = function(e) "")` · `r format(Sys.time(), '%d %B %Y, %H:%M')`
</div>
